### 2021-10-11 paper/output/document/threeflags.tex
cleaned fixed

%
\begin{isabellebody}%
\setisabellecontext{threeflags}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
The literature on Kantian ethics is expansive and complicated. To focus my thesis on the contributions 
of automated ethics to Kantian thought, I make the following choices.

$\textbf{Choice to Formalize the FUL}$

I am only studying formalizations of Kant's first formulation of the categorical imperative,
the formula of universal law (FUL), because it is the most formal and thus the easiest to formalize and implement. 
Onora O'Neill \cite{actingonprinciple}\footnote{p. 33} explains that the formalism of the FUL allows 
for greater precision in philosophical arguments analyzing its implications and power. This precision 
is particularly useful in a computational context because any formalism necessarily makes its content 
precise. The FUL's existing precision reduces ambiguity, allowing me to remain faithful to Kant's writing and 
philosophical interpretations of it. Precision reduces the need to make choices to resolve debates 
and ambiguities. Some of these choices may be well-studied and grounded in literature, 
but some may be unique to formalizing the FUL and thus understudied. Minimizing these choices minimizes 
arbitrariness in my formalization and puts it on solid philosophical footing. Given that this thesis is a proof-of-concept, 
the formalism of the FUL is attractive because it reduces both the computational and philosophical complexity of my work.

While some criticize the FUL for its formalism and percieved ``sterility" \cite{actingonprinciple}, 
Kantian constructivists embrace it. My project is not committed to Kantian constructivism; I argue that computational
ethics is a valuable tool for any ethicist, with a focus on general Kantian ethics. Nonetheless, Kantian constructivists may find the focus on 
the FUL particularly appealing.

@@

@@

My definition of a maxim is inspired by Onora O'Neill's work on maxims. I will defend my representation
below and consider an additional component that Patricia Kitcher argues for.

@@

Kitcher \cite{whatisamaxim} begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
behind performing the maxim. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal pair. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.

@@

Kantians debate the correct interpretation of the formula of universal law because Kant, 
at times, appears to interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
interpretation, broadly accepted as correct within the philosophical community \cite{ebelsduggan}\footnote{p. 177}.
Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
she believes that the text partially supports this interpretation, her argument is philosophical and 
derives its strength from the plausibility of the practical contradiction interpretation.

Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
same time will that it become a universal law” \cite{groundwork}\footnote{(G: 4:421)}. To determine if a maxim can be willed as a 
universal law, one must use the “universalizability test,” which requires imagining a world in which 
everyone for all of time has willed the maxim. If willing the maxim in such a world generates a contradiction, 
then the action is prohibited. There are three interpretations of what sort of contradiction is necessary: 
(1) the teleological view, prohibiting actions that conflict with some assumed teleological end when 
universalized, (2) the logical contradiction view, prohibiting maxims that are logically impossible 
when universalized, and (3) the practical contradiction view, prohibiting maxims that are self-defeating 
when universalized.

@@

The practical contradiction interpretation not only addresses the problems with the first two 
interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
%:%19=7%:%
%:%20=8%:%
%:%21=9%:%
%:%22=10%:%
%:%23=11%:%
%:%24=12%:%
%:%25=13%:%
%:%26=14%:%
%:%27=15%:%
%:%28=16%:%
%:%29=17%:%
%:%30=18%:%
%:%31=19%:%
%:%32=20%:%
%:%33=21%:%
%:%34=22%:%
%:%35=23%:%
%:%36=24%:%
%:%37=25%:%
%:%38=26%:%
%:%39=27%:%
%:%40=28%:%
%:%41=29%:%
%:%42=30%:%
%:%43=31%:%
%:%44=32%:%
%:%45=33%:%
%:%46=34%:%
%:%47=35%:%
%:%48=36%:%
%:%49=37%:%
%:%50=38%:%
%:%51=39%:%
%:%52=40%:%
%:%53=41%:%
%:%54=42%:%
%:%55=43%:%
%:%56=44%:%
%:%57=45%:%
%:%58=46%:%
%:%59=47%:%
%:%60=48%:%
%:%61=49%:%
%:%62=50%:%
%:%63=51%:%
%:%64=52%:%
%:%65=53%:%
%:%66=54%:%
%:%67=55%:%
%:%68=56%:%
%:%69=57%:%
%:%70=58%:%
%:%71=59%:%
%:%72=60%:%
%:%73=61%:%
%:%74=62%:%
%:%75=63%:%
%:%76=64%:%
%:%77=65%:%
%:%78=66%:%
%:%79=67%:%
%:%80=68%:%
%:%81=69%:%
%:%82=70%:%
%:%83=71%:%
%:%84=72%:%
%:%85=73%:%
%:%86=74%:%
%:%87=75%:%
%:%88=76%:%
%:%89=77%:%
%:%90=78%:%
%:%91=79%:%
%:%92=80%:%
%:%93=81%:%
%:%94=82%:%
%:%95=83%:%
%:%96=84%:%
%:%97=85%:%
%:%98=86%:%
%:%99=87%:%
%:%100=88%:%
%:%101=89%:%
%:%102=90%:%
%:%103=91%:%
%:%104=92%:%
%:%105=93%:%
%:%106=94%:%
%:%107=95%:%
%:%108=96%:%
%:%109=97%:%
%:%110=98%:%
%:%111=99%:%
%:%112=100%:%
%:%113=101%:%
%:%114=102%:%
%:%115=103%:%
%:%116=104%:%
%:%117=105%:%
%:%118=106%:%
%:%119=107%:%
%:%120=108%:%
%:%121=109%:%
%:%122=110%:%
%:%123=111%:%
%:%124=112%:%
%:%125=113%:%
%:%126=114%:%
%:%127=115%:%
%:%128=116%:%
%:%129=117%:%
%:%130=118%:%
%:%131=119%:%
%:%132=120%:%
%:%133=121%:%
%:%134=122%:%
%:%135=123%:%
%:%136=124%:%
%:%137=125%:%
%:%138=126%:%
%:%139=127%:%
%:%140=128%:%
%:%141=129%:%
%:%142=130%:%
%:%143=131%:%
%:%144=132%:%
%:%145=133%:%
%:%146=134%:%
%:%147=135%:%
%:%148=136%:%
%:%149=137%:%
%:%150=138%:%
%:%151=139%:%
%:%152=140%:%
%:%153=141%:%
%:%154=142%:%
%:%155=143%:%
%:%156=144%:%
%:%157=145%:%
%:%158=146%:%
%:%159=147%:%
%:%160=148%:%
%:%161=149%:%
%:%162=150%:%
%:%163=151%:%
%:%164=152%:%
%:%165=153%:%
%:%166=154%:%
%:%167=155%:%
%:%168=156%:%
%:%169=157%:%
%:%170=158%:%
%:%171=159%:%
%:%172=160%:%
%:%173=161%:%
%:%174=162%:%
%:%175=163%:%
%:%176=164%:%
%:%177=165%:%
%:%178=166%:%
%:%179=167%:%
%:%180=168%:%
%:%181=169%:%
%:%182=170%:%
%:%183=171%:%
%:%184=172%:%
%:%185=173%:%
%:%186=174%:%
%:%187=175%:%
%:%188=176%:%
%:%189=177%:%
%:%190=178%:%
%:%191=179%:%
%:%192=180%:%
%:%193=181%:%
%:%194=182%:%
%:%195=183%:%
%:%196=184%:%
%:%197=185%:%
%:%198=186%:%
%:%199=187%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{threeflags}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\begin{isamarkuptext}%
$\textbf{Choice to Formalize the FUL}$

In \emph{Groundwork of the Metaphysics of Morals}, Kant presents three formulations, or versions, 
of what he calls the ``supreme law of morality." I will focus on the first of these three formulations, 
and below I explain the formulations and defend my choice.

Kant argues that if  morality 
exists, it must take the form of a categorical imperative or a law that holds unconditionally. Categorical
imperatives are contrasted with hypothetical imperatives, which take the form of conditionals as in, 
``If I want to get good grades, I must study hard." Hypothetical imperatives only have force so long
as the antecedent holds, but the categorical imperative is unconditionally binding $\cite[28]{groundwork}$. In the first 
half of \emph{Groundwork}, Kant examines what the categorical imperative, if such a thing exists and has force,
must be. He concludes that there are three ``formulations" of the categorical imperative, or three ways 
of articulating the supreme law of morality.

The first formulation of the categorical imperative is the
formula of universal law (FUL), which reads, ``act only according to that maxim through which you can 
at the same time will that it become a universal law." $\cite[34]{groundwork}$ This formulation
generates the universalizability test, which ``tests" the moral value of a maxim by 
imagining a world in which it becomes a universal law and attempting to will the maxim in that world. The 
second formulation of the categorical imperative is the formula of humanity (FUH): ``So act that you use humanity, 
in your own person, as well as in the person of any other, always at the same time as an end, never merely 
as a means." $\cite[41]{groundwork}$. This formulation is often understood as requiring us to 
acknowledge and respect the dignity of every other person. The third formulation of the categorical 
imperative is the formula of autonomy (FOA), which Korsgaard summarizes in her introduction to the Groundwork 
as, ``we should so act that we may think of ourselves as legislating universal laws through our 
maxims." $\cite[28]{korsgaardintro}$ While closely related to the FUL, the FOA presents morality as the activity of 
perfectly rational agents in an ideal ``kingdom of ends," guided by what Kant calls the ``laws of freedom."

I choose to focus on formalizations of Kant's first formulation of the categorical imperative,
the formula of universal law (FUL), because it is the most formal and thus the easiest to formalize and implement. 
Onora O'Neill explains that the formalism of the FUL allows 
for greater precision in philosophical arguments analyzing its implications and power $\cite[33]{actingonprinciple}$. This precision 
is particularly useful in a computational context because any formalism necessarily makes its content 
precise. The FUL's existing precision reduces ambiguity, allowing me to remain faithful to Kant's writing and 
philosophical interpretations of it. Precision reduces the need to make choices to resolve debates 
and ambiguities. Some of these choices may be well-studied and grounded in literature, 
but some may be unique to formalizing the FUL and thus understudied. Minimizing these choices minimizes 
arbitrariness in my formalization and puts it on solid philosophical footing. Given that this thesis is a proof-of-concept, 
the formalism of the FUL is attractive because it reduces both the computational and philosophical complexity of my work.

While some criticize the FUL for its formalism and percieved ``sterility" $\cite[33]{actingonprinciple}$, 
Kantian constructivists embrace it $\cite[173]{ebelsduggan}$. My project is not committed to Kantian constructivism. 
I believe that computational ethics is likely a valuable tool for any ethicist, and I make the case 
for Kantian ethics specifically. Nonetheless, Kantian constructivists may find the focus on 
the FUL particularly appealing.

@@

The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
the agent acts on $\cite[16]{groundwork}$. Modern Kantians differ in their interpretations of this definition. The naive view 
is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
to Aristotle's logos, which includes these components and information about the circumstances and methods 
of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
defend my choice.

@@

My definition of a maxim is inspired by O'Neill's work on maxims. I will defend my representation
below and consider an additional component that Kitcher argues for.

@@

Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
behind performing the maxim \cite{whatisamaxim}. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

While Kitcher's conception of a maxim captures Kant's idea of acting for duty's own sake, I will not implement it 
because it is not necessary for putting maxims through the FUL. Indeed, Kitcher acknowledges that 
O'Neill's formulation suffices for the universalizability test, but is not the general notion of a maxim.
In order to pass the maxim through the FUL, it suffices to know the circumstance, act, and goal. The FUL
derives the motive that Kitcher bundles into the maxim, so automating the FUL does not require 
including a motive. The ``input" to the FUL is the circumstance, act, goal tuple. My project takes 
this input and returns the motivation that the dutiful, moral agent would adopt. Additionally, doing
justice to the rich notion of motive requires modelling the operation of practical reason itself, 
which is outside the scope of this project. My work focuses on the universalizability test, but future work that 
models the process of practical reason may use my implementation of the FUL as a ``library." Combined 
with a logic of practical reason, an implementation of the FUL can move from evaluating a maxim to 
evaluating an agent's behavior, since that's when ``acting from duty" starts to matter.

@@

Kantians debate the correct interpretation of the formula of universal law because Kant appears to 
interpret the universalizability test in different ways. My project uses Korsgaard's practical contradiction 
interpretation, broadly accepted as correct within the philosophical community $\cite[177]{ebelsduggan}$.
Below, I briefly reconstruct Korsgaard's argument for the practical contradiction interpretation. While 
she believes that the text partially supports this interpretation, her argument is philosophical and 
derives its strength from the plausibility of the practical contradiction interpretation.

Recall that the formula of universal law is “act only in accordance with that maxim through which you can at the 
same time will that it become a universal law” $\cite[4:421]{groundwork}$. To determine if a maxim can be willed as a 
universal law, one must use the “universalizability test,” which requires imagining a world in which 
everyone for all of time has willed the maxim. If willing the maxim in such a world generates a contradiction, 
then the action is prohibited. There are three interpretations of what sort of contradiction is necessary: 
(1) the teleological view, prohibiting actions that conflict with some assumed teleological end when 
universalized, (2) the logical contradiction view, prohibiting maxims that are logically impossible 
when universalized, and (3) the practical contradiction view, prohibiting maxims that are self-defeating 
when universalized.

@@

The practical contradiction interpretation not only addresses the problems with the first two 
interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
%:%19=9%:%
%:%20=10%:%
%:%21=11%:%
%:%22=12%:%
%:%23=13%:%
%:%24=14%:%
%:%25=15%:%
%:%26=16%:%
%:%27=17%:%
%:%28=18%:%
%:%29=19%:%
%:%30=20%:%
%:%31=21%:%
%:%32=22%:%
%:%33=23%:%
%:%34=24%:%
%:%35=25%:%
%:%36=26%:%
%:%37=27%:%
%:%38=28%:%
%:%39=29%:%
%:%40=30%:%
%:%41=31%:%
%:%42=32%:%
%:%43=33%:%
%:%44=34%:%
%:%45=35%:%
%:%46=36%:%
%:%47=37%:%
%:%48=38%:%
%:%49=39%:%
%:%50=40%:%
%:%51=41%:%
%:%52=42%:%
%:%53=43%:%
%:%54=44%:%
%:%55=45%:%
%:%56=46%:%
%:%57=47%:%
%:%58=48%:%
%:%59=49%:%
%:%60=50%:%
%:%61=51%:%
%:%62=52%:%
%:%63=53%:%
%:%64=54%:%
%:%65=55%:%
%:%66=56%:%
%:%67=57%:%
%:%68=58%:%
%:%69=59%:%
%:%70=60%:%
%:%71=61%:%
%:%72=62%:%
%:%73=63%:%
%:%74=64%:%
%:%75=65%:%
%:%76=66%:%
%:%77=67%:%
%:%78=68%:%
%:%79=69%:%
%:%80=70%:%
%:%81=71%:%
%:%82=72%:%
%:%83=73%:%
%:%84=74%:%
%:%85=75%:%
%:%86=76%:%
%:%87=77%:%
%:%88=78%:%
%:%89=79%:%
%:%90=80%:%
%:%91=81%:%
%:%92=82%:%
%:%93=83%:%
%:%94=84%:%
%:%95=85%:%
%:%96=86%:%
%:%97=87%:%
%:%98=88%:%
%:%99=89%:%
%:%100=90%:%
%:%101=91%:%
%:%102=92%:%
%:%103=93%:%
%:%104=94%:%
%:%105=95%:%
%:%106=96%:%
%:%107=97%:%
%:%108=98%:%
%:%109=99%:%
%:%110=100%:%
%:%111=101%:%
%:%112=102%:%
%:%113=103%:%
%:%114=104%:%
%:%115=105%:%
%:%116=106%:%
%:%117=107%:%
%:%118=108%:%
%:%119=109%:%
%:%120=110%:%
%:%121=111%:%
%:%122=112%:%
%:%123=113%:%
%:%124=114%:%
%:%125=115%:%
%:%126=116%:%
%:%127=117%:%
%:%128=118%:%
%:%129=119%:%
%:%130=120%:%
%:%131=121%:%
%:%132=122%:%
%:%133=123%:%
%:%134=124%:%
%:%135=125%:%
%:%136=126%:%
%:%137=127%:%
%:%138=128%:%
%:%139=129%:%
%:%140=130%:%
%:%141=131%:%
%:%142=132%:%
%:%143=133%:%
%:%144=134%:%
%:%145=135%:%
%:%146=136%:%
%:%147=137%:%
%:%148=138%:%
%:%149=139%:%
%:%150=140%:%
%:%151=141%:%
%:%152=142%:%
%:%153=143%:%
%:%154=144%:%
%:%155=145%:%
%:%156=146%:%
%:%157=147%:%
%:%158=148%:%
%:%159=149%:%
%:%160=150%:%
%:%161=151%:%
%:%162=152%:%
%:%163=153%:%
%:%164=154%:%
%:%165=155%:%
%:%166=156%:%
%:%167=157%:%
%:%168=158%:%
%:%169=159%:%
%:%170=160%:%
%:%171=161%:%
%:%172=162%:%
%:%173=163%:%
%:%174=164%:%
%:%175=165%:%
%:%176=166%:%
%:%177=167%:%
%:%178=168%:%
%:%179=169%:%
%:%180=170%:%
%:%181=171%:%
%:%182=172%:%
%:%183=173%:%
%:%184=174%:%
%:%185=175%:%
%:%186=176%:%
%:%187=177%:%
%:%188=178%:%
%:%189=179%:%
%:%190=180%:%
%:%191=181%:%
%:%192=182%:%
%:%193=183%:%
%:%194=184%:%
%:%195=185%:%
%:%196=186%:%
%:%197=187%:%
%:%198=188%:%
%:%199=189%:%
%:%200=190%:%
%:%201=191%:%
%:%202=192%:%
%:%203=193%:%
%:%204=194%:%
%:%205=195%:%
%:%206=196%:%
%:%207=197%:%
%:%208=198%:%
%:%209=199%:%
%:%210=200%:%
%:%211=201%:%
%:%212=202%:%
%:%213=203%:%
%:%214=204%:%
%:%215=205%:%
%:%216=206%:%
%:%217=207%:%
%:%218=208%:%
%:%219=209%:%
%:%220=210%:%
%:%221=211%:%
%:%222=212%:%
%:%223=213%:%
%:%224=214%:%
%:%225=215%:%
%:%226=216%:%
%:%227=217%:%
%:%228=218%:%
%:%229=219%:%
%:%230=220%:%
%:%231=221%:%
%:%232=222%:%
%:%233=223%:%
%:%234=224%:%
%:%235=225%:%
